---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rocrateR: RO-Crate R Package Wrapper

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/rocrateR)](https://CRAN.R-project.org/package=rocrateR)
[![R-CMD-check](https://github.com/villegar/ro-crate-r/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/villegar/ro-crate-r/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/villegar/ro-crate-r/graph/badge.svg)](https://app.codecov.io/gh/villegar/ro-crate-r)
<!-- badges: end -->

The goal of rocrateR is to provide an R package for creating, manipulating and reading RO-Crates. Latest supported version 1.2 of the specification. 

## Installation

You can install the development version of rocrateR like so:

``` r
# install.packages("remotes")
remotes::install_github("villegar/ro-crate-r", "main")

OR

remotes::install_github("ResearchObject/ro-crate-r", "main")
```

## First RO-Crate

The following command creates an RO-Crate Metadata descriptor (`ro-crate-metadata.json`). This should be stored inside the root (`./`) of your RO-Crate.

```{r example}
# library(rocrateR)
my_first_ro_crate <- rocrateR::rocrate()
```

This object is a list with the basic components of an RO-Crate. It can be visualised in the console with the `print` command:

```{r}
print(my_first_ro_crate)
```

